$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-06 paper/paper.tex
Replace references to sections in type safety with references to theorems

   \item \textbf{Semantics}: \autoref{semantics} provides an operational semantics for the \picalc{}, prior to any typing.
   This operational semantics is given as a reduction relation on processes (\autoref{operational-semantics}).
   The reduction relation tracks at the type level the channel the communication occurs on, so that this information can then be used to state subject reduction --- aka type preservation (\autoref{subject-reduction}).
   The reduction relation is defined modulo structural congruence (\autoref{structural-congruence}) --- a relation that acts as a quotient type that removes unnecessary syntactic minutiae introduced by the syntax of the \picalc{}.
 \end{itemize}

@@

    Benefits of typing with leftovers include: removing the need for extrinsic context splits, which are rendered unnecessary; and for the first time we can state theorems like \textbf{weakening} (\autoref{thm:weakening}) and \textbf{strengthening} (\autoref{thm:strengthening}) in the linear \picalc{}.    
  \end{itemize}
  \item \textbf{Machine verified proofs of subject reduction and auxiliary theorems}:
  \autoref{type-safety} details the type safety properties of our \picalc{} with leftovers.
  Leftover typing allows \emph{framing} (\autoref{thm:framing}), \emph{weakening} (\autoref{thm:weakening}) and \emph{strengthening} (\autoref{thm:strengthening}) theorems to be stated.
  We use these to prove \emph{subject congruence} (\autoref{subject-congruence}), and together with \emph{substitution} (\autoref{substitution}), to prove \emph{subject reduction} (\autoref{subject-reduction}).

@@

The operational semantics of the \picalc{} is defined as a reduction relation \textsc{Reduces} $\reduce{c}$ indexed by the channel $c$ on which communication occurs (\autoref{fig:reduction}).
We keep track of channel $c$ so we can state subject reduction (\autoref{subject-reduction}).
We distinguish between channels that are created inside of the process ($\constr{internal}$) and channels that are created outside ($\constr{external}\ i$, where $i$ is the index of the channel variable).

@@

\begin{nitheorem}[Subject reduction]
  Let $P$ be well typed in $\types{\gamma}{\Gamma}{P}{\Xi}$ and reduce such that $P \reduce{c} Q$.
  \begin{itemize}
    \item If $c$ is $\constr{internal}$, then $\types{\gamma}{\Gamma}{Q}{\Xi}$.
    \item If $c$ is $\constr{external} \; i$ and $\containsusage{\Gamma}{i}{\lio}{\Delta}$, then $\types{\gamma}{\Delta}{Q}{\Xi}$.
  \end{itemize}
\end{nitheorem}

>>>>

   \item \textbf{Semantics}: \autoref{semantics} provides an operational semantics for the \picalc{}, prior to any typing.
   This operational semantics is given as a reduction relation on processes (\autoref{operational-semantics}).
   The reduction relation tracks at the type level the channel the communication occurs on, so that this information can then be used to state subject reduction --- aka type preservation (\autoref{thm:subject-reduction}).
   The reduction relation is defined modulo structural congruence (\autoref{structural-congruence}) --- a relation that acts as a quotient type that removes unnecessary syntactic minutiae introduced by the syntax of the \picalc{}.
 \end{itemize}

@@

    Benefits of typing with leftovers include: removing the need for extrinsic context splits, which are rendered unnecessary; and for the first time we can state theorems like \textbf{weakening} (\autoref{thm:weakening}) and \textbf{strengthening} (\autoref{thm:strengthening}) in the linear \picalc{}.    
  \end{itemize}
  \item \textbf{Machine verified proofs of subject reduction and auxiliary theorems}:
  \autoref{type-safety} details the type safety properties of our \picalc{} with leftovers.
  Leftover typing allows \emph{framing} (\autoref{thm:framing}), \emph{weakening} (\autoref{thm:weakening}) and \emph{strengthening} (\autoref{thm:strengthening}) theorems to be stated.
  We use these to prove \emph{subject congruence} (\autoref{thm:subject-congruence}), and together with \emph{substitution} (\autoref{thm:substitution}), to prove \emph{subject reduction} (\autoref{thm:subject-reduction}).

@@

The operational semantics of the \picalc{} is defined as a reduction relation \textsc{Reduces} $\reduce{c}$ indexed by the channel $c$ on which communication occurs (\autoref{fig:reduction}).
We keep track of channel $c$ so we can state subject reduction (\autoref{thm:subject-reduction}).
We distinguish between channels that are created inside of the process ($\constr{internal}$) and channels that are created outside ($\constr{external}\ i$, where $i$ is the index of the channel variable).

@@

\begin{nitheorem}[Subject reduction]
  \label{thm:subject-reduction}
  Let $P$ be well typed in $\types{\gamma}{\Gamma}{P}{\Xi}$ and reduce such that $P \reduce{c} Q$.
  \begin{itemize}
    \item If $c$ is $\constr{internal}$, then $\types{\gamma}{\Gamma}{Q}{\Xi}$.
    \item If $c$ is $\constr{external} \; i$ and $\containsusage{\Gamma}{i}{\lio}{\Delta}$, then $\types{\gamma}{\Delta}{Q}{\Xi}$.
  \end{itemize}
\end{nitheorem}
